Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-10-25 Tables/mdlContactGeneral.tex
meta General LM added
theory meta added
REML fixed

\caption{\label{tab:intergroupGeneralTbl}Intergroup General}

@@

(Intercept) & 70.50**** [66.06, 74.94] &  & 67.62**** [64.16, 71.08] &  & 64.83**** [61.50, 68.16] &  & 67.44**** [61.71, 73.17] &  & 63.72**** [59.42, 68.01] &  & 56.30**** [51.58, 61.02] & \\

@@

OutgroupInteraction &  &  &  &  &  &  & 2.48**** [ 1.36,  3.59] & 1.07 [ 0.59,  1.54] & 2.99*** [ 1.45,  4.54] & 0.11 [ 0.07, 0.16] & 5.63**** [ 3.97,  7.29] & 0.21 [ 0.15, 0.27]\\
NonOutgroupInteraction &  &  &  &  &  &  & 0.43 [-0.68,  1.54] & 0.16 [-0.32,  0.63] & 0.01 [-0.76,  0.78] & 0.01 [-0.03, 0.05] & 0.34 [-0.49,  1.18] & 0.02 [-0.02, 0.05]\\

@@

\hspace{1em}$\sigma^2$ &  &  &  &  &  &  & 69.92 &  & 77.46 &  & 88.1 & \\
\hspace{1em}$\tau_{00}$ &  &  &  &  &  &  & 164.13 (PID) &  & 488.38 (PID) &  & 366.51 (PID) & \\
\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & \makecell[c]{48.94 (PID.OutgroupInteraction)\\ 7.23 (PID.NonOutgroupInteraction)} &  & \makecell[c]{40.53 (PID.OutgroupInteraction)\\ 3.43 (PID.NonOutgroupInteraction)} & \\
\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & \makecell[c]{-0.72 (PID.OutgroupInteraction)\\ 0.12 (PID.NonOutgroupInteraction)} &  & \makecell[c]{-0.70 (PID.OutgroupInteraction)\\-0.28 (PID.NonOutgroupInteraction)} & \\
\hspace{1em}$\rho_{00}$ &  &  &  &  &  &  &  &  & 0.00 (PID.OutgroupInteraction-NonOutgroupInteraction) &  & 0.26 (PID.OutgroupInteraction-NonOutgroupInteraction) & \\

@@

@@

\hspace{1em}$R^{2 (a)}$ & 0.540 / 0.459 &  & 0.094 / 0.069 &  & 0.088 / 0.047 &  & 0.006 / 0.703 &  & 0.003 / 0.817 &  & 0.026 / 0.708 & \\
\hspace{1em}AIC &  &  &  &  &  &  & 8788 &  & 36476 &  & 29074 & \\
\hspace{1em}BIC &  &  &  &  &  &  & 8814 &  & 36542 &  & 29137 & \\
\hspace{1em}ICC &  &  &  &  &  &  & 0.7013 &  & 0.8167 &  & 0.7007 & \\

>>>>

\caption{\label{tab:intergroupGeneralTblWide}Intergroup General}

@@

(Intercept) & 70.50**** [66.06, 74.94] &  & 67.62**** [64.16, 71.08] &  & 64.83**** [61.50, 68.16] &  & 74.12**** [ 56.74, 91.49] &  & 67.05**** [ 57.37, 76.73] &  & 60.36**** [ 46.45, 74.27] & \\

@@

OutgroupInteraction &  &  &  &  &  &  & 2.48**** [  1.37,  3.59] & 1.07 [ 0.59, 1.54] & 2.83*** [  1.28,  4.38] & 0.11 [ 0.07, 0.16] & 5.57**** [  3.90,  7.23] & 0.21 [ 0.15, 0.27]\\
NonOutgroupInteraction &  &  &  &  &  &  & 0.44 [ -0.67,  1.55] & 0.16 [-0.32, 0.63] & 0.02 [ -0.76,  0.79] & 0.01 [-0.03, 0.05] & 0.36 [ -0.48,  1.19] & 0.02 [-0.02, 0.05]\\

@@

\hspace{1em}OutgroupInteractionM &  &  &  &  &  &  & 0.99 [-26.61, 28.59] & 1.65 [-4.27, 7.57] & 26.53** [  8.61, 44.46] & 0.00 [-0.03, 0.03] & 14.14 [ -2.19, 30.48] & 0.00 [-0.03, 0.03]\\
\hspace{1em}NonOutgroupInteractionM &  &  &  &  &  &  & -4.82 [-30.26, 20.63] & -1.08 [-7.02, 4.86] & -8.32 [-22.98,  6.35] & 0.00 [-0.03, 0.03] & -2.75 [-20.00, 14.50] & 0.00 [-0.03, 0.03]\\
\hspace{1em}$\sigma^2$ &  &  &  &  &  &  & 69.91 &  & 77.42 &  & 88.1 & \\
\hspace{1em}$\tau_{00}$ &  &  &  &  &  &  & 179.20 (PID) &  & 318.62 (PID) &  & 199.47 (PID) & \\
\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & \makecell[c]{48.96 (PID.OutgroupInteractionC)\\ 7.40 (PID.NonOutgroupInteractionC)} &  & \makecell[c]{40.64 (PID.OutgroupInteractionC)\\ 3.44 (PID.NonOutgroupInteractionC)} & \\

@@

\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & \makecell[c]{-0.39 (PID.OutgroupInteractionC)\\ 0.33 (PID.NonOutgroupInteractionC)} &  & \makecell[c]{-0.26 (PID.OutgroupInteractionC)\\ 0.05 (PID.NonOutgroupInteractionC)} & \\
\hspace{1em}$\rho_{00}$ &  &  &  &  &  &  &  &  & 0.03 (PID.OutgroupInteractionC-NonOutgroupInteractionC) &  & 0.24 (PID.OutgroupInteractionC-NonOutgroupInteractionC) & \\

@@

\hspace{1em}$R^{2 (a)}$ & 0.540 / 0.459 &  & 0.094 / 0.069 &  & 0.088 / 0.047 &  & 0.009 / 0.722 &  & 0.050 / 0.818 &  & 0.049 / 0.717 & \\
\hspace{1em}AIC &  &  &  &  &  &  & 8778 &  & 36461 &  & 29065 & \\
BIC &  &  &  &  &  &  & 8814 &  & 36539 &  & 29140 & \\
ICC &  &  &  &  &  &  & 0.7193 &  & 0.8082 &  & 0.703 & \\

### 2022-10-25 manuscript.tex
REML fixed

% Figures
\begin{figure}
  \caption{Contact Hypothesis}
  \label{fig:ContactHypothesis}
  \centering\includegraphics[width=\textwidth]{Figures/forestParametricGeneralComb.png}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricGeneralLm.png}
  %\end{subfigure}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricFEGeneralLmer.png}
  %\end{subfigure}
  \caption*{Note: \\
  (a) summary of regression results from the aggregated contact and interaction quality data.\\
  (b) summary of mixed models results of the contemporaneous contact effects.\\
  General: Fixed effects meta analytic results are presented for completeness only.}
\end{figure}

\begin{figure}
  \caption{Core Need Fulfillment}
  \label{fig:AllportNeedFulfillment}
  \centering\includegraphics[width=\textwidth]{Figures/forestParametricTheoryComb.png}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryQualityCore.png}
  %\end{subfigure}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCore.png}
  %\end{subfigure}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCoreQuality.png}
  %\end{subfigure}
  \caption*{Note: \\
  (a) Core Need Fulfillment predicting Interaction Quality.\\
  (b) Core Need Fulfillment predicting Outgroup Attitudes.\\
  (c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.\\
  General: Fixed effects meta analytic results are presented for completeness only.}
\end{figure}

\begin{figure}
  \caption{Robustness Analyses}
  \label{fig:Robustness}
  \centering\includegraphics[width=\textwidth]{Figures/forestParametricRobustnessComb.png}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustContact.png}
  %\end{subfigure}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustSDT.png}
  %\end{subfigure}
  \caption*{Note: \\
  (a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).\\
  (b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).\\
  General: Fixed effects meta analytic results are presented for completeness only.}
\end{figure}

>>>>

% Figures
\begin{figure}
  \caption{Contact Hypothesis}
  \label{fig:ContactHypothesis}
  \centering\includegraphics[width=\textwidth]{Figures/forestParametricREMLGeneralLmer.png}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricGeneralLm.png}
  %\end{subfigure}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricFEGeneralLmer.png}
  %\end{subfigure}
  \caption*{Note: \\
  Summary of mixed models results of the contemporaneous contact effects.\\
  General: Random effects meta analytic results are presented for completeness.}
\end{figure}

\begin{figure}
  \caption{Core Need Fulfillment}
  \label{fig:AllportNeedFulfillment}
  \centering\includegraphics[width=\textwidth]{Figures/forestParametricTheoryComb.png}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryQualityCore.png}
  %\end{subfigure}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCore.png}
  %\end{subfigure}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCoreQuality.png}
  %\end{subfigure}
  \caption*{Note: \\
  (a) Core Need Fulfillment predicting Interaction Quality.\\
  (b) Core Need Fulfillment predicting Outgroup Attitudes.\\
  (c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.\\
  General: Random effects meta analytic results are presented for completeness.}
\end{figure}

\begin{figure}
  \caption{Robustness Analyses}
  \label{fig:Robustness}
  \centering\includegraphics[width=\textwidth]{Figures/forestParametricRobustnessComb.png}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustContact.png}
  %\end{subfigure}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustSDT.png}
  %\end{subfigure}
  \caption*{Note: \\
  (a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).\\
  (b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).\\
  General: Random effects meta analytic results are presented for completeness.}
\end{figure}
